---
title: "BIOL432_Assignment 6"
author: "SiruiZHAO"
date: "2023-02-14"
output: html_document
---

Part II

First, we need to load library
```{r}
library(annotater)
library(BiocManager)
library(annotate)
library(ape)
library(dplyr)
```

Then, copy and paste the sequence we found
```{r}
Sequences <- "GCCTGATGGAGGGGGATAACTACTGGAAACGGTAGCTAATACCGCATGAC
CTCGCAAGAGCAAAGTGGGGGACCTTAGGGCCTCACGCCATCGGATGAAC
CCAGATGGGATTAGCTAGTAGGTGGGGTAATGGCTCACCTAGGCGACGAT
CCCTAGCTGGTCTGAGAGGATGACCAGCCACACTGGAACTGAGACACGGT
CCAGACTCCTACGGGAGGCAGCAGTGGGGAATATTGCACAATGGGCGCAA"
```

```{r}
#remove special character
Sequences <- gsub("[\r\n]", "", Sequences)
```

There will be 33 sequences matched when we choose 5 hits.
```{r}
seqBLAST <- blastSequences(paste(Sequences),as = 'data.frame',
                            hitListSize = 5, timeout = 600)
```
```{r}
nrow(seqBLAST)
```

Now, we can select some columns and make them a new data frame. To compare these sequences, I sorted the data in decreasing order on Hsp_score. Because it represents the strength of the match, and higher scores mean stronger matches. We can also compare them based on Hsp_evalue, and smaller values generally indicate stronger matches. In hit_def, it shows most of them come from Yersinia but are not human. The Hsp_gaps shows the number of gaps between the query sequence and its match, in which we all got 0 gaps. 

```{r}
results <- seqBLAST %>%
  select(Hit_def, Hit_accession, Hit_len, Hsp_score, Hsp_evalue, Hsp_gaps, Hsp_qseq) %>%
  arrange(desc(Hsp_score), .by_group = TRUE)
head(results)
```

Thanks!
